Floquet-Drude Conductivity in Dressed Quantum Hall Systems

### 2021-07-01 paper/v1.0/sections/4_floquet_fermi_golden.tex
Add changes

In this section we are going to derive the Floquet Fermi goldern rule for previously derived quantum Floquet states using $t-t'$ formalism \cite{bruus04}.

>>>>

In this section we are going to derive the Floquet Fermi goldern rule for previously derived quantum Floquet states using $t-t'$ formalism \cite{wackerl20,grifoni98,sambe75,peskin93,althorpe97}.
